### 2012-03-20 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

Additionally, PathType contains a list of special functions that were called with an argument of PathType type. The motivation is that in some cases of function calls, we want to know that the function call is performed with an instance of PathType because then, we can determine a type of the function call more precisely. Those special functions are built-in functions \texttt{data}, \texttt{min}, \texttt{max}, \texttt{avg}, \texttt{sum}, \texttt{distinct-values}.

@@

@@

>>>>

Additionally, PathType contains a list of special functions that were called with an argument of PathType type. The motivation is that in some cases of function calls, we want to know that the function call is performed with an instance of PathType because then, we can determine a type of the function call more precisely. Those special functions are built-in functions \texttt{data}, \texttt{min}, \texttt{max}, \texttt{avg}, \texttt{sum}, \texttt{distinct-values}. \todo{DOPLNIT}

@@

\begin{figure}
\label{FIG_syntax_tree_1_types}
\caption{Sample syntax tree 1 after the static analysis of types.}
\includegraphics[scale=0.6]{syntax_tree_1_types.eps}
\end{figure}

@@

Figure \ref{FIG_syntax_tree_1_types} shows the syntax tree from Figure \ref{FIG_syntax_tree_1} after the static analysis of expression types. The types are shown in red color. Note that the node representing \texttt{zero-or-one} function call is of a PathType type, as well as its argument. It is so, because the function returns its argument unchanged, and thus, we included the function in the special functions list in the PathType definition.

Also note, that the function call node of \texttt{local:convert} in the FLWOR return clause has \texttt{zero-or-one} cardinality and the FLWOR node has \texttt{zero-or-more} cardinality. The change of cardinality is a result of the for unbinding shown in Algorithm \ref{ALG_function_create_for_unbound_type}.
